Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-08-20 awipev-CO2.Rmd
adding RMSE on property plots

```{r pHs comparaison durafet spectro, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / durafet
fit <- lmodel2(data = d_all,  ph_s_dur_temp_fb ~ ph_dur_corr , nperm = 99)

p_dura_spectro <-  ggplot(d_all,aes(x=ph_dur_corr, y= ph_s_dur_temp_fb, label = month))+
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
    coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH durafet", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
p_dura_spectro
```

<!-- ### **Spectro / seaFET** -->

```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / seafet
# fit <- lmodel2(data = d_all,  ph_s_sf_temp_insi ~ pHint_tot_sf , nperm = 99)
#
# p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_insi, label = month))+
#   geom_text( aes(color=factor(month))) +
#   scale_color_discrete(guide = "none")+
#  geom_abline(slope=1, intercept =0, linetype = "dashed") +
#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
#   labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
#                      "; Slope =", signif( fit$regression.results[2,3], 3),
#                      "; P =", signif(fit$P.param, 3))) +
#   theme(aspect.ratio=1,plot.title = element_text(size=7)) +
#     coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
#   labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw()
# p_sf_spectro
```

>>>>

```{r pHs comparaison durafet spectro, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / durafet
lm <- lm2(x = d_all$ph_s_dur_temp_fb, y = d_all$ph_dur_corr)

p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = month)) +
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 3))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH durafet", y="pH spectro", color = "Months")
p
```

```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
# Spectro / seafet
lm <- lm2(x = d_all$ph_s_sf_temp_insi, y = d_all$pHint_tot_sf)

p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = month)) +
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_abline(slope=1, intercept =0, linetype = "dashed") +
  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste("pH spectro vs pH seafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
                     "; P =", signif(lm$fit$P.param, 3),
                     "; RMSE = ", signif(lm$rmse, 1))) +
  theme_bw() +
  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
  labs(x="pH spectro", y="pH seafet", color = "Months")
p
```
